some title

### 2018-01-05 2018/paper.tex
todo corr done

\begin{figure}[ht!]
\begin{center}
\includegraphics{images/corr_def.pdf}
\label{fig:corr_def}
\caption{Random vector $X$ of length $\sigma_X$ and random vector $Y$ of length $\sigma_Y$, $\cos \varphi$ is the angle between $X$ and $Y$.}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics{images/corr_proj.pdf}
\label{fig:corr_proj}
\caption{Random vector $Y$ projected onto random vector $X$.}
\end{center}
\end{figure}

@@

\begin{proof}
Firstly, we consider the case when $\hat \beta_2 > 0$ so the main picuture is of the form depicted in Figure~\ref{fig:corr_pos_base}.
It has been shown earlier that the correlation coefficient squared represents the angle betweem two random vectors.

\begin{figure}[ht!]
\begin{center}
\includegraphics{images/corr_eq_positive.pdf}
\label{fig:corr_pos_base}
\caption{Vectors $x$, $y$ and $\mathbf{1}$.}
\end{center}
\end{figure}

@@

In order to get the angle between $y$ and $\hat y$ we should start with regressing $y$ on $Lin(x, \mathbf{1})$.
Then the only thing thing left is to project $\hat y$ onto $Lin^{\perp}\mathbf{1}$ since the $y$ vector has already been projected.
The result of this step is shown in Figure~\ref{fig:corr_pos_yhatc}.

@@

todo: whole picture, $\beta_2<0$

>>>>

\begin{figure}[ht!]
\begin{center}
\includegraphics{images/corr_def.pdf}
\caption{Random vector $X$ of length $\sigma_X$ and random vector $Y$ of length $\sigma_Y$, $\cos \varphi$ is the angle between $X$ and $Y$.}
\label{fig:corr_def}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics{images/corr_proj.pdf}
\caption{Random vector $Y$ projected onto random vector $X$.}
\label{fig:corr_proj}
\end{center}
\end{figure}

@@

\begin{proof}
Firstly, we consider the case when $\hat \beta_2 > 0$ so the main picuture is of the form depicted in Figure~\ref{fig:corr_pos_base}.
It has been shown earlier that the correlation coefficient represents the angle betweem two random vectors.
So in order to complete the proof we need to find the appropriate angles and compare them.

\begin{figure}[h!]
\center{\includegraphics{images/corr_eq_positive.pdf}}
\caption{Vectors $x$, $y$ and $\mathbf{1}$.}
\label{fig:corr_pos_base}
\end{figure}

@@

In order to get the angle between $y$ and $\hat y$ we should start with regressing $y$ on $Lin(x, \mathbf{1})$.
Then the only thing thing left is to project $\hat y$ onto $Lin^{\perp}\mathbf{1}$ since the $y$ vector has already been projected.
Note that the projected $\hat y$ falls onto tha span of vector $x - \bar x \cdot \mathbf{1}$ as it can be decomposed into a sum $a x + b \mathbf{1}$ where $a, b \in \mathbb{R}$.
$a x$ is projected in the same way as $x$ and $b \mathbf{1}$ yields zero when projected onto the orthogonal space.
The result of this step is shown in Figure~\ref{fig:corr_pos_yhatc}.

@@

Since the projection of $\hat y$ lies exactly on the span of vector $x - \bar x \cdot \mathbf{1}$, we can conclude that $cos \varphi = \cos \varphi '$ and to put it another way $\sCorr(x,y) = \sCorr(y, \hat y)$.

Now consider the case when $\hat \beta_2 < 0$.
Note that the sign of $\beta_1$ does not influence the correlation coefficient sign.
The only difference is that now $\hat y$ is projected onto the span of  $x - \bar x \cdot \mathbf{1}$ not on this vector itself while the projections of $x$ and $y$ remain the same.
Looking at Figure~\ref{fig:corr_negative} we deduce that the angle betwween $y$ and $\hat y$ is compelement to the angle between $x$ and $y$.
Using trigonometric properties, we simplify $\cos(180^{\circ} - \varphi) = -\cos\varphi$ which in turn implies $\sCorr(x,y) = -\sCorr(y,\hat y)$.

\begin{figure}[ht!]
\begin{center}
\includegraphics{images/corr_eq_negative.pdf}
\label{fig:corr_negative}
\caption{Case of $\beta_2 < 0$.}
\end{center}
\end{figure}
\end{proof}
